Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-28 Draft/Draft.Rmd
A bit of intro and playing with heatmaps

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes. Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.

@@

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1111 pollinator species and 6248 of plant-pollinator interactions counted. For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].

Plants were grouped into reproductive strategies [justify and explain the process]

Pollintors were grouped into guilds, because [justify and explain, it's important to convince the reader that Order level for pollinators and FG for plants makes sense].

@@

1) over and under represented motifs
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
str(d)
head(d)

ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
  geom_histogram(color="black", fill="white")+
  facet_wrap(~motif)+
  theme_bw()+
  labs(x="Sizeclass percentile")

# Motifs tend to be over- and under-represensented in real networks

>>>>

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019]. Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.

Several studies have evaluated the structure of plant-pollinator interactions. These studies have found common structural properties across networks that can help the understanding of the determinats of biodiversity [@bastolla2009]. One of the major findings is the nested structure of mutualistic networks [@bascompte2003] which describes the topological structure where the specialist interact with subgroups of the interacting species of the generalist. Further, the degree distribution (number of links per species) of plant-pollinator networks have been shown to generally follow a power-law truncated distribution [@jordano2003]. Moreover, at the species level ...

Trait matching

@@

**Plant-pollinator studies**

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1111 pollinator species and 6248 of pairwise interactions registered. For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].

**Plant and pollinator functional groups**

First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies. This was done with the help of hierarchical cluster analysis by using the trait dataset compiled in Lanuza et al., (unpublished). This dataset consisted on x floral, x reproductive and x vegetative traits (Table S2). For this, we calculated the distance of the different functional traits with the function gowdis from the package FD version 1.0-12 (Laliberté et al., 2014) with the method ward.D2 used for non-squared distances (Murtagh & Legendre, 2014). All the numerical traits were previously scaled. Finally, we applied a hierarchical cluster analysis with the function hclust from the R stats package version 4.0.5 and calculated the optimal number of clusters with the function kgs from the package maptree version 1.4-7 (White & Gramacy, 2009).

Second, pollinators were grouped into functional groups based on taxonomic rank. We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) they main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38). Hence, we grouped pollinators into 6 functional groups: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.

**Meso-scale analysis**

@@

1) over and under represented motifs
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

#ggplot(d %>% filter(motif != 1), aes(percentil_sizeclass))+
#  geom_histogram(color="black", fill="white")+
#  facet_wrap(~motif)+
#  theme_bw()+
#  labs(x="Sizeclass percentile")
#
# Motifs tend to be over- and under-represensented in real networks
